
\chapter{Abstract}
 
In this thesis, we extensively study the task of rumor detection in Twitter. Twitter is a microblogging service which is already used by millions of users. Users can publish and exchange information with short tweets through all kinds of Twitter clients: website, mobile phone or email. These advantages make Twitter an ideal media for spreading breaking news and false rumors.Therefore, automatic detecting rumors in social media has recently become a trending topic. Early research mostly focused on the rumors during one or several specific events like earthquake or terrorist attack. But in our work, we study on the general types of impact rumors. Additionally most previous works for rumor detection are modeled with static features, like the content of tweets or propagation features, and they ignored the fact which those features can change with the development of the event by time.

We build up a system with Random Forest and the dynamic model proposed by Ma et al.~\cite{ma2015detect} called Dynamic Series-Time Structure (DSTS) with the temporal features and their varieties over time which is named TS-RF. We adapt a series of mathematical epidemiological models (i.e., SpikeM, SIS and SEIZ) to model the propagation patterns of rumors and add them as temporal features for TS-RF. To improve the time series model's performance at early stage of the events, we develop a single tweet's credibility scoring model with CNN+LSTM, which can predict a single tweet as rumor related or news related, with 81.20\% accuracy. The output of the single tweet's credibility scoring model which we called CreditScore, is a novel and then is shown to be the best feature for time series model TS-RF in our extensive experiments. Overall, our time series rumor detecting model (TS-RF) reaches over 90\% accuracy and out-performs state-of-the-art models (e.g., DSTS) in the study of 48 hours. Last but not least, to the best of our knowledge, we are the first work to evaluate the temporal fluctuations performance of rumor features over time.


